Universal Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-10-20 SI.tex
Add SI figures for raw data
Add figures for SI

% Created 2017-10-05 Thu 16:11
% Intended LaTeX compiler: pdflatex
\documentclass[manuscript=suppinfo,email=true,hyperref=true,keywords=false]{achemso}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{longtable}
\usepackage{footnote}
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes}

@@

From literatures, it is often desired to extract the ``dielectric
constant'' of a 2D material from the 3D macroscopic dielectric constant
\cite{Matthes_2016,Laturia_2018}. As discussed in the main text and
other studies\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D},
the definition of the 2D ``dielectric constant'' (in particular, its
in-plane components) is questionable, due to the locality of
electrostatic screening of the 2D materials. Here we show that, in
addition to the ambiguous definition of the 2D dielectric constant,
such approach requires the precise determination of the 2D layer
thickness $\delta_{\mathrm{2D}}$, which makes it impractical.

In brief, the hypothetical 2D dielectric constant
$\varepsilon_{\mathrm{2D}}$ comes from the planar limit of the
Maxwell-Garnett effective medium theory \cite{Markel_2016}, and can be
expressed by means of the macroscopic dielectric constant
$\varepsilon_{\mathrm{SL}}$ of the superlattice:

\begin{eqnarray}
  \label{eq:MG-effect-1}
  &\varepsilon_{\mathrm{SL}}^{\parallel} &= f \varepsilon_{\mathrm{2D}}^{\parallel} + (1 - f)\\
  \label{eq:MG-effect-2}
  &(\varepsilon_{\mathrm{SL}}^{\perp})^{-1} &= f (\varepsilon_{\mathrm{2D}}^{\perp})^{-1} + (1-f)
\end{eqnarray}
where $f=\delta_{\mathrm{2D}}/L$ is the volume fraction of the 2D
material in the superlattice. The major issue when using such rescale
relations comes from the determination of $\delta_{\mathrm{2D}}$,
which is not well defined for a 2D material. To eliminate the modeling
error caused by the \texttt{a priori} parameter selection of
$\delta_{\mathrm{2D}}$, we perform the calculation of
$\varepsilon_{\mathrm{SL}}$ of group 6 TMDCs against different $L$, and use
least-square fitting to extract both $\varepsilon_{\mathrm{2D}}$ and
$\delta_{\mathrm{2D}}$, as shown in Figure \ref{fig:rescale-prb}.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/SI-rescale-PRB.pdf}
  \caption{ Calculated (blue dots) and fitted
    (orange broken lines) $\varepsilon_{\mathrm{SL}}$ as function of
    $L$ for the group 6 TMDCs:
    \textbf{a}. MoS$_{2}$. \textbf{b}. MoSe$_{2}$. \textbf{c}.
    MoTe$_{2}$. \textbf{d}. WS$_{2}$. \textbf{e}. WSe$_{2}$. \textbf{f}.
    WTe$_{2}$. The extracted values of $\varepsilon_{\mathrm{2D}}$ and
    $\delta_{\mathrm{2D}}$ are shown in each subfigure.}
  \label{fig:rescale-prb}
\end{figure}

@@

We study the polarizabilties of group 6 TMDCs to demonstrate the
dependency between the 2D polarizability $\alpha$ and the superlattice
length $L$, which is shown in Figure \ref{fig:eps-L-all} \todo{Which
  method?}.  In all cases, we observe that the calculated
polarizability converges when $L>$15 \AA{}, in good agreement with our
conclusion in main text. The lower bound of $L_{\mathrm{min}}$ for the
convergence of $\alpha$ can be viewed as the minimal distance that
overlap of induced charge density from image layers is negligible. In
practice, any superlattice size larger than $L_{\mathrm{min}}$ can be
used for calculating the intrinsic 2D dielectric nature through the
polarizability, however to reduce the computational cost, especially
at the HSE level, we typically choose a superlattice size no larger
than 35 \AA{}.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/SI-eps-L-all.pdf} 
  \caption{Calculated value of $\varepsilon_{\mathrm{SL}}^{\parallel}$
    (top left axis), $\varepsilon_{\mathrm{SL}}^{\perp}$ (bottom left
    axis), $\alpha^{\parallel}$ (top right axis) and $\alpha^{\perp}$
    (bottom right axis) of various group 6 TMDCs. In all cases, the
    polarizability  converges when $L>$15 \AA{}}
  \label{fig:eps-L-all}
\end{figure}

\subsection{Depdence of bandgap}
\label{sec:pol-2D-2}

@@

We also investigate the relation of 2D polarizabilities with
difference choices of \textit{ab initio} bandgaps. It is widely
accepted that the PBE method, while gives quantitative predictions of
the dielectric response of 2D and layered materials, tends to
underestimate the bangap
\cite{Kumar_2016_PRB,Kumar_2016_jpcc}. \todo{complete the discussion
  for HSE?}  Indeed, changing the choice of $E_{\mathrm{g}}$ yields
different regression relation with $1/\alpha^{\parallel}$, as shown in
Figure \ref{fig:alpha-Eg-diff}. We see that due to the underestimation
of PBE bandgap, the slope of linear regression is larger than that
from HSE-bandgap. We also observe that the $1/\alpha-E_{\mathrm{g}}$
relation is better presented by using the minimal HSE bandga than the
minimal PBE bandgap, due to higher regression $R^{2}$ coefficient of
the former. We note that the higher $R^{2}$ coefficient observed using
the direct PBE bandgap than the minimal PBE bandgap may be solely
caused by the fact that the direct bandgap of 2D materials on the PBE
level is closer to the HSE bandgap. From the random phase
approximation theory of dielectric response, the polarizability is
contributed by all possible transition between valence and conduction
bands, with the minimal bandgap as the least possible transition. In
this sense, $\alpha^{\parallel}$ is mostly like to be associated with
the minimal, not direct bandgap, as also observed in the original Moss
relation. We also examine the validity of such statement based on the
analysis of the Computational 2D Materials Database (C2DB)
\cite{Haastrup_2018}, as will be discussed in the following sections.

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-gpaw-data.pdf}
  \caption{Validation the linear relation between \textbf{a}
    $1/\alpha^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and \textbf{b}
    $\alpha^{\perp}-\delta_{\mathrm{2D}}^{\mathrm{cov}}$ on the C2DB
    2D material database. }
  \label{fig:gpaw-alpha-relation}
\end{figure}

Due to the high computation complexity of dielectric response
calculations on the HSE level, our 2D material database is limited to
about 50 types of materials. It is desirable to validate our proposed
relations on a even larger scale database. \todo{Add comments for the
  C2DB database}. We select 210 semiconducting 2D materials from the
C2DB database with a HSE bandgap larger than 0.5 eV and extracted the
2D polarizabilities calculated on the PBE level. The propsed linear
relations between $1/\alpha^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$
and $\alpha^{\perp}-\delta_{\mathrm{2D}}^{\mathrm{cov}}$ are also
valid, as shown in Figure \ref{fig:gpaw-alpha-relation}. Excellent
linear correlation is observed in both cases, with the $R^{2}$
coefficient larger than 0.9, indicating the existence of the universal
description of 2D dielectric nature through the proposed relations
with the 2D polarizabilities. We note that the slope of linear
regression is slightly different from the our proposed relation from
the dielectric response on HSE level, due to the fact that the
macroscopic dielectric constant $\varepsilon_{\mathrm{SL}}$ calculated
on the PBE level is about 5\% lower. Despite the minor deviation of
the slope of linear regression, the analysis on the C2DB database
supports our understanding of the universal dielectric nature of 2D
materials.

@@

Next we investigate the influence of choice of $E_{\mathrm{g}}$ on the
regression of $\alpha^{\parallel}-E_{\mathrm{g}}$ relation. Figure
\ref{fig:SI-gpaw-alpha-Eg-all} shows $1/\alpha^{\parallel}$ from the
C2DB database as a function of minimal and direct bandgap calculated
on PBE, HSE and GW levels.\todo{to be more specific?} We observe,
although the regression $R^{2}$ coefficient in all cases are around
0.9, the $\alpha^{\parallel}-E_{\mathrm{g}}$ is better described using
the HSE and GW bandgaps than the PBE bandgaps. On the other hand,
using indirect or minimal bandgaps on the same level gives almost
identical regression slope. The observations are in good agreement
with our calculations on the HSE level discussed in Section
\ref{sec:pol-2D-2}. In combination with the physical contribution of
$E_{\mathrm{g}}$ to the dielectric screening, we conclude that the
minimal bandgap should be used for quantitative prediction of the
in-plane 2D polarizability. The prediction is greatly improved when
more accurate theory level for bandgap is used (for instance, HSE and GW).

@@

From Figures \ref{fig:gpaw-2D-quantities-1} to
\ref{fig:gpaw-2D-quantities-3} we can see that none of the above
quantities have apparent relation with the 2D polarizabilities, as
compared with the bandgap and covalent thickness proposed in the main
text. \todo{add some more explanation}

@@

\subsection{Detailed derivations from Eq. 10}
\label{sec:theory-1}

Here we will first show how Eq. 10 in the main text is
derived. Treating the in-plane wavefunctions as plane wave with form
$\psi^{\parallel}(\rho) \propto e^{i \mathbf{k \rho}}$, the matrix
element of
$<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{qr}}|\psi_{\mathrm{c}}(\mathbf{k+q})>$,
when $\mathbf{q}=(0, 0, q_{z})$, becomes\cite{Hybertsen_1987}:
\begin{equation}
  \begin{aligned}
    \label{eq:matrix-z}
  <\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{qr}}|\psi_{\mathrm{c}}(\mathbf{k+q})>
  &= \frac{1}{A} \int dx \int dy
  e^{i(\mathbf{-k \rho} - \mathbf{q \rho} + \mathbf{(k+q) \rho})}
  \int (\psi^{\perp})^{*}_{\mathrm{v}}(\mathbf{k})e^{-iq_{z}z}\psi^{\perp}_{\mathrm{c}}(\mathbf{k+q})\\
  &= <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|e^{-iq_{z}z}|\psi^{\perp}_{\mathrm{c}}(\mathbf{k+q})>
  \end{aligned}
\end{equation}
Note that the states perpendicular are bound, the integral is
meaningful only when $\mathbf{k=k+q}$ \cite{davies_physics_1997}. By
performing the Taylor expansion of
$e^{-i\mathbf{qr}} \approx 1 - i\mathbf{qr}$, we get:
\begin{equation}
  \begin{aligned}
    \label{eq:matrix-z}
    <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|e^{-iq_{z}z}|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>
    &\approx <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})> -
    iq_{z} <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>\\
    &= -iq_{z} <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>
   \end{aligned}
\end{equation}
plug this into Eq. 7 in main text and express the summation over
$k_{x}$ and $k_{y}$ in a continuous form within the Brillouin Zone, we
arrive at Eq. 10 in main text.

Although the exact form for $\psi^{\perp}$ depends on the exact
distribution of $V(z)$, without loss of generality we can assume the
electrons are confined in a potential well of width $\delta$, which is
the typical treatment for semiconductor QWs
\cite{ihn_semiconductor_2009}. The allowed bound states inside the
confined region generally has wave vector
$k_{z} \propto n \pi / \delta$. With the total energy
$E_{n}(\mathbf{k}) = {\displaystyle \frac{\hbar^{2} (k_{x}^{2} +
    k_{y}^{2})}{2 m^{\parallel}} + \frac{\hbar^{2} n^{2} \pi^{2}}{2
    m^{\perp} \delta^{2}}}$, where $m^{\parallel}$ and $m^{\perp}$ are
the effective masses parallel and perpendicular to the 2D
plane. Therefore the denominator of Eq. 10 becomes independent of
$\mathbf{k}$, that
$E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k}) =
(n_{\mathrm{c}}^{2} - n_{\mathrm{v}}^{2}) {\displaystyle
  \frac{\hbar^{2} \pi^{2}}{2 m^{\perp} \delta^{2}}}$. On the other
hand, the numerator
$<\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>$
is proportional to the confinement length $\delta$ (can be seen using
particle-in-box solution\cite{davies_physics_1997}). In combination,
the individual terms of the summation in the right hand of Eq. 10 is
independent of neither $E_{\mathrm{g}}$ nor \textbf{k}, proving that
$\alpha^{\perp}$ is independent of the band gap.

Finally we will show the $\alpha^{\perp}$ is related to the
confinement length $\delta$, or equivalent the thickness of the 2D
material. For simplicity we assume $\psi^{\parallel}$ is the solution
of a particle confined inside an infinite potential well of width
$\delta$ with the form $\psi \propto \sin(\frac{n\pi}{\delta})$. At 0
K, the only non-zero contribution for the transition between band
$n_{\mathrm{v}}$ and $n_{\mathrm{c}}$ corresponds with in-plane wave
vector $\mathbf{k}_{\rho}$ within the range of $k_{\mathrm{F}}^{\mathrm{v}}$ to
$k_{\mathrm{F}}^{\mathrm{c}}$, the Fermi vectors of each band. Therefore we have:
\begin{equation}
  \begin{aligned}
    \alpha^{\perp} &\propto \delta^{4} m^{\perp} \int
    d^{2}\mathbf{k}_{\rho}
    \frac{f(\psi_{\mathrm{v}}(\mathbf{k}_{\rho}))
      -f(\psi_{\mathrm{v}}(\mathbf{k}_{\rho})) }{n_{\mathrm{c}}^{2} -
      n_{\mathrm{v}}^{2}}\\
    &= \delta^{4} m^{\perp} \sum_{\mathrm{c, v}}\pi \frac{
      (k_{\mathrm{F}}^{\mathrm{c}})^{2} -
        (k_{\mathrm{F}}^{\mathrm{v}})^{2}}{n_{\mathrm{c}}^{2} -
        n_{\mathrm{v}}^{2}}
  \end{aligned}
\end{equation}
Since the Fermi wave vector for band \textit{i} follows
${\displaystyle
  \frac{\hbar^{2}(k_{\mathrm{F}}^{i})^{2}}{2m^{\parallel}}} +
{\displaystyle \frac{\hbar^{2} n_{i}^{2} \pi^{2}}{2m^{\perp}
    \delta^{2}}} = E_{\mathrm{F}}$, we have
$ (k_{\mathrm{F}}^{\mathrm{c}})^{2} -
(k_{\mathrm{F}}^{\mathrm{v}})^{2} \propto (n_{\mathrm{c}}^{2} -
n_{\mathrm{v}}^{2}) {\displaystyle
  \frac{m^{\parallel}}{m^{\perp}}}$. Note that in the particle-in-box
model, the energy levels for a sub-nm QW will be at the order of 10
eV, which allows only few states inside the QW. Combine with the fact
that the strongest transition comes from the lowest bands
\cite{davies_physics_1997}, we can finally show:
\begin{equation}
  \label{eq:alpha-perp-L}
  \alpha^{\perp} \propto m^{\parallel} \delta^{2}
\end{equation}
Apart from the power of $\delta$, this explains our observation
$\alpha^{\perp}$ is related with the thickness of a 2D material. We
note the power law of $\delta^{2}$ instead of $\delta$ is
inevitable. The atomic polarizabilities of free particles inside a 1D
infinite QW, finite QW or harmonic QW all show dependency with
$\delta^{4}$, where $\delta$ is the length of confinement or effective
harmonic length of the QW \cite{Fowler_1984,Maize_2011}. Since the 2D
polarizability is the molecular polarizability divided by the area,
such approach will always yield $\alpha^{\perp} \propto \delta^{2}$
regardless of the Hamiltonian used. To accurately model the
$\alpha^{\perp}$ we need a better model for the confinement in
z-direction than simple square potential well, which may be
tedious. Nevertheless the simple model presented here still captures
the bandgap-indepent and thickness-related feature of
$\alpha^{\perp}$, supporting our findings in the main text.

\subsection{Detailed discussion for main text Eq. 14 }
\label{sec:theory-2}

>>>>

% Created 2017-10-05 Thu 16:11
% Intended LaTeX compiler: pdflatex
\documentclass[manuscript=suppinfo,email=true,hyperref=true,keywords=false]{achemso}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{ltablex}
\usepackage{footnote}
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes}

@@

From literatures, it is often desired to extract the ``dielectric
constant'' of a 2D material from the 3D macroscopic dielectric
constant of the superlattice, where the layers are periodic along of
x,y directions but separated by a vacuum layer between its images
\cite{Matthes_2016,Laturia_2018}. As discussed in the main text, the
definition of the 2D ``dielectric constant'' (in particular, its
in-plane components) is questionable, due to the locality of
electrostatic screening of the 2D materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Here we show
that, in addition to the ambiguous definition of the 2D dielectric
constant, such approach requires the precise determination of the 2D
layer thickness $\delta_{\mathrm{2D}}$, which makes it impractical.

In brief, the hypothetical 2D dielectric constant
$\varepsilon$ comes from the planar limit of the
Maxwell-Garnett effective medium theory \cite{Markel_2016}, and can be
expressed by means of the macroscopic dielectric constant
$\varepsilon_{\mathrm{SL}}$ of the superlattice:

\begin{eqnarray}
  \label{eq:MG-effect-1}
  &\varepsilon_{\mathrm{SL}}^{\parallel} &= f \varepsilon_{\mathrm{2D}}^{\parallel} + (1 - f)\\
  \label{eq:MG-effect-2}
  &(\varepsilon_{\mathrm{SL}}^{\perp})^{-1} &= f /\varepsilon_{\mathrm{2D}}^{\perp} + (1-f)
\end{eqnarray}
where $f=\delta/L$ is the volume fraction of the 2D
material in the superlattice. The major issue when using such rescale
relations comes from the determination of $\delta_{\mathrm{2D}}$. To
eliminate the modeling error caused by the \textit{a priori} parameter
selection of $\delta$, we perform the calculation of
$\varepsilon_{\mathrm{SL}}$ of group 6 TMDCs against different $L$,
and use least-square fitting to extract both
$\varepsilon$ and $\delta$, as shown in
Figure \ref{fig:rescale-prb}.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/SI-rescale-PRB.pdf}
  \caption{ Calculated (blue dots) and fitted
    (orange broken lines) $\varepsilon_{\mathrm{SL}}$ as function of
    $L$ for the group 6 TMDCs:
    \textbf{a}. MoS$_{2}$. \textbf{b}. MoSe$_{2}$. \textbf{c}.
    MoTe$_{2}$. \textbf{d}. WS$_{2}$. \textbf{e}. WSe$_{2}$. \textbf{f}.
    WTe$_{2}$. The extracted values of $\varepsilon_{\mathrm{2D}}$ and
    $\delta$ are shown in each subfigure.}
  \label{fig:rescale-prb}
\end{figure}

@@

We study the polarizabilties of group 6 TMDCs to demonstrate the
dependency between the 2D polarizability $\alpha$ and the superlattice
length $L$, which is shown in Figure \ref{fig:eps-L-all}.  In all cases, we observe that the calculated
polarizability converges when $L>$15 \AA{}, in good agreement with our
conclusion in main text. The lower bound of $L_{\mathrm{min}}$ for the
convergence of $\alpha$ can be viewed as the minimal distance that
overlap of induced charge density from image layers is negligible. In
practice, any superlattice size larger than $L_{\mathrm{min}}$ can be
used for calculating the intrinsic 2D dielectric nature through the
polarizability, however to reduce the computational cost, especially
at the HSE06 level, we typically choose a superlattice size no larger
than 35 \AA{}.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/SI-eps-L-all.pdf} 
  \caption{Calculated value of $\varepsilon_{\mathrm{SL}}^{\parallel}$
    (top left axis), $\varepsilon_{\mathrm{SL}}^{\perp}$ (bottom left
    axis), $\alpha^{\parallel}$ (top right axis) and $\alpha^{\perp}$
    (bottom right axis) of various group 6 TMDCs corresponding to
    Figure 1 in main text. In all cases, the polarizability converges
    when $L>$15 \AA{}}
  \label{fig:eps-L-all}
\end{figure}

\subsection{Dependence of bandgap}
\label{sec:pol-2D-2}

@@

We also investigate the relation of 2D polarizabilities with
difference choices of \textit{ab initio} bandgaps. It is widely
accepted that the PBE exchange correlation, tends to underestimate the
bangap \cite{Heyd_2005,Kumar_2016_PRB,Kumar_2016_jpcc}.  Indeed,
changing the choice of $E_{\mathrm{g}}$ yields different regression
relation with $1/\alpha^{\parallel}$, as shown in Figure
\ref{fig:alpha-Eg-diff}. We see that due to the underestimation of PBE
bandgap, the slope of linear regression is larger than that from
HSE-bandgap. We also observe that the $1/\alpha-E_{\mathrm{g}}$
relation is better presented by using the minimal HSE bandga than the
minimal PBE bandgap, due to higher regression $R^{2}$ coefficient of
the former. We note that the higher $R^{2}$ coefficient observed using
the direct PBE bandgap than the minimal PBE bandgap may be solely
caused by the fact that the direct bandgap of 2D materials on the PBE
level is closer to the HSE bandgap. From the random phase
approximation theory of dielectric response, the polarizability is
contributed by all possible transition between valence and conduction
bands, with the minimal bandgap as the least possible transition. In
this sense, $\alpha^{\parallel}$ is mostly like to be associated with
the minimal, not direct bandgap, as also observed in the original Moss
relation. We also examine the validity of such statement based on the
analysis of the Computational 2D Materials Database (C2DB)
\cite{Haastrup_2018}, as will be discussed in the following sections.

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-gpaw-data.pdf}
  \caption{Validation the linear relation between \textbf{a}
    $1/\alpha^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and \textbf{b}
    $\alpha^{\perp}-\delta_{\mathrm{cov}}$ on the C2DB 2D material
    database, corresponding to Figure 3b and 3c in main text.}
  \label{fig:gpaw-alpha-relation}
\end{figure}

Due to the high computation complexity of dielectric response
calculations on the HSE level, our 2D material database is limited to
about 50 types of materials. It is desirable to validate our proposed
relations on a even larger scale database. We select over 230
semiconducting 2D materials from the C2DB database with a GW bandgap
larger than 0.05 eV and extracted the 2D polarizabilities calculated
on the PBE level. The propsed linear relations between
$1/\alpha^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and
$\alpha^{\perp}-\delta_{\mathrm{cov}}$ are also valid,
as shown in Figure \ref{fig:gpaw-alpha-relation}. Excellent linear
correlation is observed in both cases, with the $R^{2}$ coefficient
larger than 0.9, indicating the existence of the universal description
of 2D dielectric nature through the proposed relations with the 2D
polarizabilities. We note that the slope of linear regression is
slightly different from the our proposed relation from the dielectric
response on HSE06 level, due to the fact that the macroscopic
dielectric constant $\varepsilon_{\mathrm{SL}}$ calculated on the PBE
level is about slightly difference. Despite the minor deviation of the
slope of linear regression, the analysis on the C2DB database supports
our understanding of the universal dielectric nature of 2D materials.

@@

Next we investigate the influence of choice of $E_{\mathrm{g}}$ on the
regression of $\alpha^{\parallel}-E_{\mathrm{g}}$ relation. Figure
\ref{fig:SI-gpaw-alpha-Eg-all} shows $1/\alpha^{\parallel}$ from the
C2DB database as a function of minimal and direct bandgap calculated
on PBE, HSE06 and GW levels. We observe,
although the regression $R^{2}$ coefficient in all cases are around
0.9, the $\alpha^{\parallel}-E_{\mathrm{g}}$ is better described using
the HSE and GW bandgaps than the PBE bandgaps. On the other hand,
using indirect or minimal bandgaps on the same level gives almost
identical regression slope. The observations are in good agreement
with our calculations on the HSE level discussed in Section
\ref{sec:pol-2D-2}. In combination with the physical contribution of
$E_{\mathrm{g}}$ to the dielectric screening, we conclude that the
minimal bandgap should be used for quantitative prediction of the
in-plane 2D polarizability. The prediction is greatly improved when
more accurate theory level for bandgap is used (for instance, HSE and GW).

@@

From Figures \ref{fig:gpaw-2D-quantities-1} to
\ref{fig:gpaw-2D-quantities-3} we can see that none of the above
quantities have apparent relation with the 2D polarizabilities, as
compared with the bandgap and covalent thickness proposed in the main
text.

@@

\subsection{Detailed derivations for Eq. 5a and 5b}
\label{sec:theory-1}

Here we will first show how Eq. 5a and 5b in the main text are
derived. Taking the limit that $L\to\infty$, when
$\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Therefore
$\alpha^{\parallel}$ and $\alpha^{\perp}$ at 0 K can be unified by the
same equation:
\begin{equation}
  \label{eq:alpha-RPA}
  \alpha = \frac{2e^{2}}{|q|^{2}A} \sum_{\mathrm{k,c,v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
where the direction is determined by $\mathbf{q}$.

For the in-plane component, $\alpha^{\parallel}$, $e^{-i\mathbf{qr}}$
is independent of $z$, therefore the integral in
$|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}$
becomes the independent of $\psi^{\perp}$, due to the
orthogonality. Present the summation of k-space into integral, and further
combining with the Bloch wave representation and the k-p
theory\cite{Jiang_2017_Eg_Eb}, we arrive at Eq. 5a.

For Eq. 5b, treating the in-plane wavefunctions as plane wave with
form $\psi^{\parallel}(\rho) \propto e^{i \mathbf{k \rho}}$, the
matrix element of
$<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{qr}}|\psi_{\mathrm{c}}(\mathbf{k+q})>$,
when $\mathbf{q}=(0, 0, q_{z})$, becomes\cite{Hybertsen_1987}:
\begin{equation}
  \begin{aligned}
    \label{eq:matrix-z}
  <\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{qr}}|\psi_{\mathrm{c}}(\mathbf{k+q})>
  &= \frac{1}{A} \int dx \int dy
  e^{i(\mathbf{-k \rho} - \mathbf{q \rho} + \mathbf{(k+q) \rho})}
  \int (\psi^{\perp})^{*}_{\mathrm{v}}(\mathbf{k})e^{-iq_{z}z}\psi^{\perp}_{\mathrm{c}}(\mathbf{k+q})\\
  &= <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|e^{-iq_{z}z}|\psi^{\perp}_{\mathrm{c}}(\mathbf{k+q})>
  \end{aligned}
\end{equation}
Note that the states perpendicular are bound, the integral is
meaningful only when $\mathbf{k=k+q}$ \cite{davies_physics_1997}. By
performing the Taylor expansion of
$e^{-i\mathbf{qr}} \approx 1 - i\mathbf{qr}$, we get:
\begin{equation}
  \begin{aligned}
    \label{eq:matrix-z}
    <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|e^{-iq_{z}z}|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>
    &\approx <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})> -
    iq_{z} <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>\\
    &= -iq_{z} <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>
   \end{aligned}
\end{equation}
plug this into Eq. \ref{eq:alpha-RPA} and express the summation over
$k_{x}$ and $k_{y}$ in a continuous form within the Brillouin Zone, we
arrive at Eq. 5b in main text.

Although the exact form for $\psi^{\perp}$ depends on the exact
distribution of $V(z)$, without loss of generality we can assume the
electrons are confined in a potential well of width $\delta$, which is
the typical treatment for semiconductor QWs
\cite{ihn_semiconductor_2009}. The allowed bound states inside the
confined region generally has wave vector
$k_{z} \propto n \pi / \delta$. With the total energy
$E_{n}(\mathbf{k}) = {\displaystyle \frac{\hbar^{2} (k_{x}^{2} +
    k_{y}^{2})}{2 m^{\parallel}} + \frac{\hbar^{2} n^{2} \pi^{2}}{2
    m^{\perp} \delta^{2}}}$, where $m^{\parallel}$ and $m^{\perp}$ are
the effective masses parallel and perpendicular to the 2D
plane. Therefore the denominator of Eq. 10 becomes independent of
$\mathbf{k}$, that
$E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k}) =
(n_{\mathrm{c}}^{2} - n_{\mathrm{v}}^{2}) {\displaystyle
  \frac{\hbar^{2} \pi^{2}}{2 m^{\perp} \delta^{2}}}$. On the other
hand, the numerator
$<\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>$
is proportional to the confinement length $\delta$ (can be seen using
particle-in-box solution\cite{davies_physics_1997}). In combination,
the individual terms of the summation in the right hand of Eq. 5b is
independent of neither $E_{\mathrm{g}}$ nor \textbf{k}, proving that
$\alpha^{\perp}$ is independent of the band gap.

Finally we will show the $\alpha^{\perp}$ is related to the
confinement length $\delta$, or equivalent the thickness of the 2D
material. For simplicity we assume $\psi^{\parallel}$ is the solution
of a particle confined inside an infinite potential well of width
$\delta$ with the form $\psi \propto \sin(\frac{n\pi}{\delta})$. At 0
K, the only non-zero contribution for the transition between band
$n_{\mathrm{v}}$ and $n_{\mathrm{c}}$ corresponds with in-plane wave
vector $\mathbf{k}_{\rho}$ within the range of $k_{\mathrm{F}}^{\mathrm{v}}$ to
$k_{\mathrm{F}}^{\mathrm{c}}$, the Fermi vectors of each band. Therefore we have:
\begin{equation}
  \begin{aligned}
    \alpha^{\perp} &\propto \delta^{4} m^{\perp} \int
    d^{2}\mathbf{k}_{\rho}
    \frac{f(\psi_{\mathrm{v}}(\mathbf{k}_{\rho}))
      -f(\psi_{\mathrm{v}}(\mathbf{k}_{\rho})) }{n_{\mathrm{c}}^{2} -
      n_{\mathrm{v}}^{2}}\\
    &= \delta^{4} m^{\perp} \sum_{\mathrm{c, v}}\pi \frac{
      (k_{\mathrm{F}}^{\mathrm{c}})^{2} -
        (k_{\mathrm{F}}^{\mathrm{v}})^{2}}{n_{\mathrm{c}}^{2} -
        n_{\mathrm{v}}^{2}}
  \end{aligned}
\end{equation}
Since the Fermi wave vector for band \textit{i} follows
${\displaystyle
  \frac{\hbar^{2}(k_{\mathrm{F}}^{i})^{2}}{2m^{\parallel}}} +
{\displaystyle \frac{\hbar^{2} n_{i}^{2} \pi^{2}}{2m^{\perp}
    \delta^{2}}} = E_{\mathrm{F}}$, we have
$ (k_{\mathrm{F}}^{\mathrm{c}})^{2} -
(k_{\mathrm{F}}^{\mathrm{v}})^{2} \propto (n_{\mathrm{c}}^{2} -
n_{\mathrm{v}}^{2}) {\displaystyle
  \frac{m^{\parallel}}{m^{\perp}}}$. Note that in the particle-in-box
model, the energy levels for a sub-nm QW will be at the order of 10
eV, which allows only few states inside the QW. Combine with the fact
that the strongest transition comes from the lowest bands
\cite{davies_physics_1997}, we can finally show:
\begin{equation}
  \label{eq:alpha-perp-L}
  \alpha^{\perp} \propto \delta^{2}
\end{equation}
Apart from the power of $\delta$, this explains our observation
$\alpha^{\perp}$ is related with the thickness of a 2D material. We
note the power law of $\delta^{2}$ instead of $\delta$ is
inevitable. The atomic polarizabilities of free particles inside a 1D
infinite QW, finite QW or harmonic QW all show dependency with
$\delta^{4}$, where $\delta$ is the length of confinement or effective
harmonic length of the QW \cite{Fowler_1984,Maize_2011}. Since the 2D
polarizability is the molecular polarizability divided by the area,
such approach will always yield $\alpha^{\perp} \propto \delta^{2}$
regardless of the Hamiltonian used. To accurately model the
$\alpha^{\perp}$ we need a better model for the confinement in
z-direction than simple square potential well, which may be
tedious. Nevertheless the simple model presented here still captures
the bandgap-indepent and thickness-related feature of
$\alpha^{\perp}$, supporting our findings in the main text.
